---
title: "605 Assignment 2"
author: "simplymathematics"
date: "September 9, 2018"
output: pdf_document
---

## Assignment 2
### Problem 1
If we assume that $A^T A = A A^T$, then we must find only a single case where that is not true to prove that this is not true in general. Let A by an arbitrary 2 X 1 matrix such that 
$$
A =
\begin{bmatrix}
a_{1,1} \\
a_{2,1}
\end{bmatrix}
$$
Without loss of generality, without loss of generality, we see that the left hand side is the multiplication of a 1 X 2 matrix with a 2 X 1 matrix, which yields a scalar. Alternatively, the right hand side is a 2 x 1 multiplied by a 1 X 2, which yields a 2 X 2 matrix. These can never be equal, disproving the assumption that $A^T A = A A^T$ in general. 

However, that is true of a special type of matrix called a symmetrical matrix, because for symmetric matricies, 
$$
A^T = A
$$
We can prove the above property quite trivially for any symmetric matrix

$$
A^TA = AA^T = A^T A^T = A A 
$$
### Demonstration

Furthermore, we an demonstrate that with an R function
```{r}
demo <- function(A){
  transpose <- t(A)
  lhs <- A%*%t(A)
  rhs <- t(A)%*%A
  print(lhs)
  print(rhs)
  if (identical(lhs,rhs)){
    stop("You found a symmetric matrix. Try again!")
  }
  else{
    print("You disproved the above assumption")
  }
}
A <- matrix(c(1,2,3,1,2,3,1,2,3),nrow=3,ncol=3)
demo(A)
A2 <- matrix(c(1,1,1,1),nrow=2,ncol=2)
demo(A2)
```
## Problem 2

Write an R function to factorize a square matrix into LU or LDU. 
Because we are tasked with LU (or LDU factorization), we must pass a positive definite matrix. that will not be checked, although it's squareness will. The function returns a list of variables (L,U) in that order. In order to test the fitness of A, you need matrixcalc installed. You can install it on your machine locally by running:
```{r}
install.packages("matrixcalc")
```

```{r}
lu_factorization <- function(A){
  library(matrixcalc)
  if (nrow(A)!= ncol(A)){
    stop("Must be a square matrix!")
  }
  if (!(is.positive.definite(A,tol=1e-8))){
    stop("Must be positive definite!")
  }
  size <- nrow(A)
  L <- matrix (0, nrow = size, ncol = size)
  U <- matrix (0, nrow = size, ncol = size)
  for (i in 1:size){
    L[i,i] = 1
  }
  for ( i in 1:size ) {
        up <- i + 1
        down <- i - 1
        for ( j in 1:size ) {
            U[i,j] <- A[i,j]
            if ( down > 0 ) {
                for ( k in 1:down ) {
                    U[i,j] <- U[i,j] - L[i,k] * U[k,j]
                }
            }
        }
        if ( up <= size ) {
            for ( j in up:size ) {
                L[j,i] <- A[j,i]
                if ( down > 0 ) {
                    for ( k in 1:down ) {
                        L[j,i] <- L[j,i] - L[j,k] * U[k,i]
                    }
                }
                L[j,i] <- L[j,i] / U[i,i]
            }    
        }
  }
  answer <- list(L,U)
  return(answer)
}
A = matrix(c(2,1,1,1,2,1,1,1,2), nrow = 3, ncol = 3)
lu_factorization(A)
```

