---
title: "605 HW 3"
author: "simplymathematics"
date: "September 16, 2018"
output: html_document
---

## Homework 3
### Problem Set 1
#### 1
What is the rank of matrix A, such that 
$$
A = 
\begin{bmatrix}
1 & 2 & 3 & 4 \\
-1 & 0 & 1 & 3 \\
0 & 1 & -2 & 1 \\
5 & 4 & -2 & -3
\end{bmatrix}
$$

We know that this 4 x 4 matrix, can have, at most 4 linearly independent vectors. To determine how many linearly independent vectors there are, we find the row-reduced elchelon form using Gaussian Elimination. We can do this quite easily in R, using the rref() function from the pracma library.

```{r}
#install.packages('pracma')
A <- matrix(c(1,2,3,4,-1,0,1,3,0,1,-2,1,5,4,-2,-3),ncol=4,nrow=4)
library('pracma')
rref(A)
```

As we can see from the output, that even with row-reduction, we cannot eliminate 1 term from each column or row. Therefore, these vectors a linearly independent and the rank is 4.

#### 2

The maximum rank for an $m \times n$ where $n < m$ is $n$ and the minimum rank is 1 if the matrix is non-zero. 

#### 3 

```{r}
#install.packages('pracma')
A <- matrix(c(1,2,1,3,6,3,2,4,2),ncol=3,nrow=3)
library('pracma')
rref(A)
```
Although we can see it upon inspection, R makes it obvious that there is only 1 linearly independent vector in this matrix.

### Problem set 2

Let 
$$
A = 
\begin{bmatrix}
1 & 2 & 3 \\
0 & 4 & 5 \\
0 & 0 & 6
\end{bmatrix}
$$
Eigenvalues of the numbers that hold a special property for a given matrix such that
$$ Ax = \lambda x $$
Where $\lambda$ is a diagonal matrix and $I$ is the identity matrix such that
$$(A-\lambda I)x =0$$
and
$$\det \mid A-\lambda I\mid = 0$$
which gives us 
$$
A -\lambda I  =
\begin{bmatrix}
\lambda-1 & 2 & 3 \\
0 & \lambda-4 & 5 \\
0 & 0 & \lambda-6
\end{bmatrix}
$$
Therefore
$$
\det \mid A -\lambda I\mid  =
\det
\begin{bmatrix}
\lambda-1 & 2 & 3 \\
0 & \lambda-4 & 5 \\
0 & 0 & \lambda-6
\end{bmatrix}
$$
or
$$
\det \mid A -\lambda I\mid  = \lambda-1 \cdot \det
\begin{bmatrix}
\lambda -4 & 5 \\
0 & \lambda - 6
\end{bmatrix}
-
3 \cdot \det
\begin{bmatrix}
0 & 5 \\
0 & \lambda - 6
\end{bmatrix}
+ 
3 \cdot \det
\begin{bmatrix}
0 & \lambda -4 \\
0 & 0
\end{bmatrix}
$$
Which is the same as
$$
\det \mid A -\lambda I\mid  =
\lambda-1 \cdot \det
\begin{bmatrix}
\lambda -4 & 5 \\
0 & \lambda - 6
\end{bmatrix}
$$
or 
$$
\det \mid A -\lambda I\mid  =
(\lambda-1) \cdot (\lambda - 4) \cdot (\lambda-6)
 = 0 
$$
Which tells us that
$$
\lambda_1 = 1, \lambda_2 = 4, \lambda_3 = 6
$$

We can confirm this easily using the R packages from above
```{r}
A <- matrix(c(1,2,3,0,4,5,0,0,6),nrow=3,ncol=3)
eig(A)
```
