---
title: "605 HW 5"
author: "simplymathematics"
date: "September 30, 2018"
output: html_document
---

If we take two numbers, B and C, and assume they are randomly and uniformly distributed on the interval [0,1], we must prove that P(B)< 0 or P(B)> 1 is null. However, this is easy as it is given in the definition. Likewise, we can use R to generate a random integer B or C. 

```{r}
B <- runif(1)
C <- runif(1)

B
C
help(runif)
```

Additionally, we must show that $f(x) \geq 0$, which is true by inspection. Another condition is that  $\int_{a}^{b} f(x) = 1$ on the interval specified. The help(runif) command (or other documentation) gives us our f(x) such that 
$$ f(x) = \frac{1}{max-min}= \frac{1}{1-0}  = 1$$
or
$$ \int_{a}^{b}1\space dx = b - a = 1-0 = 1$$
## B + C < 1/2

```{r}
B <- runif(1000000)
C <- runif(1000000)
Z <- B+C
hist(Z, breaks=100)
```

Since we know that these variables are independent, their sum can be modelled as standard, symmetrical triangular distribution with peak = 1. Therefore
$$
P(B+C<\frac{1}{2}) 
$$

$$
P(x) \begin{cases}
\frac{2(x-a)}{(b-a)(b-c)} & \text{for } a < x < c \\
\frac{2(b-x)}{(b-a)(b-c)} & \text{for } c < x < b
\end{cases}
$$

where (if a = 0, b =2, and c = midpont(a,b)

$$
P(x) \begin{cases}
\frac{2(x-0)}{(2-0)(2-1)} & \text{for } a < x < c \\
\frac{2(b-x)}{(2-0)(2-1)} & \text{for } c < x < b
\end{cases}
$$

or 

$$
P(x) \begin{cases}
\frac{2x}{2} & \text{for } a < x < c \\
\frac{4-2x}{2} & \text{for } c < x < b
\end{cases}
$$
or
$$
P(x) \begin{cases}
x & \text{for } a < x < c \\
2-x & \text{for } c < x < b
\end{cases}
$$
and the cumulative distribution function for the piece [c,b]
$$
D(x) = \frac{(x-a)^2}{(b-a)(c-a)} = \frac{\frac{1}{2}^2-0^2}{(2-0)(2-1)} = \frac{1}{8}
$$ 
where x is B + C.
## BC < 1/2

The cumulative distribution function is

$$   
F(x)= \begin{cases}
  0 & \text{for }x < a \\[8pt]
  \frac{x-a}{b-a} & \text{for }a \le x \le b \\[8pt]
  1 & \text{for }x > b
  \end{cases}
$$
Therefore, the 
$$
P(x<\frac{1}{2}) = \int_{0}^{1} \frac{x-a}{b-a} dx =  \int_{0}^{1} \frac{1/2-0}{1-0}dx = \int_{0}^{1}\frac{1}{2} dx = 1/2
$$
Since this is true for both B and C, we can multiply this final number to obtain 
$$ 
\frac{1}{2} \cdot \frac{1}{2} = \frac {1}{4} 
$$

## |B-C|<1/2
If $Z= B-C$ then $W = Z + 1$  has the form $W = X + (1-Y) = X + Y' where X and Y' = 1-Y are independent, random variables on [0,1], which has a well known triangular density such that
$$
F_y(Y) = P(Y\le y) =  P(B-C < y) = 
\begin{cases}
\int_0^{1+y}\int_{x_1-y}^11dx_2dx_1 & -1 <y < 0 \\ 
1 - \int_y^1\int_0^{x_1-y}1dx_2dx_1 & 0<y<1
\end{cases}
$$
or

$$
F_y(Y) 
\begin{cases}
\frac{y^2}{2}+y+\frac{1}{2} & -1 <y < 0 \\ 
-\frac{y^2}{2}+y+\frac{1}{2} & 0<y<1
\end{cases}
$$
or 

$$
-(1/2)^2+1/2+1/2 = 1-\frac{1}{8}

$$
or 
$$ F_y(1/2) = \frac{7}{8} $$
## max{B,C} <1/2

The cumulative distribution function for one variable is

$$   
F(x)= \begin{cases}
0 & \text{for }x < a \\[8pt]
\frac{x-a}{b-a} & \text{for }a \le x \le b \\[8pt]
1 & \text{for }x > b
\end{cases}
$$
Therefore, the 
$$ P(x<\frac{1}{2}) = \int_{0}^{1} \frac{x-a}{b-a} dx =  \int_{0}^{1} \frac{1/2-0}{1-0}dx = \int_{0}^{1}\frac{1}{2} dx =\frac{1}{2}$$
Since this is true for both B and C, we can multiply this final number to obtain 
$$ 
\frac{1}{2} \cdot \frac{1}{2} = \frac {1}{4} 
$$

## min{B,C} <1/2

This is logically equivalent to  
$$ 
P(B < \frac{1}{2} \cup C < \frac{1}{2})
$$
or 
$$
P(B < \frac{1}{2}) + P(C < \frac{1}{2}) - P(B\cap C) = \frac{1}{2} + \frac{1}{2} - \frac{1}{4} = \frac{3}{4}
$$

