---
title: "605 wk 6"
author: "simplymathematics"
date: "October 6, 2018"
output: html_document
---

## 1
A bag contains several different color marbles as seen below.
```{r}
total = 54+9+75
red = 54/total
white = 9/total
blue = 75/total
```
We can then see that the probability of either of these occuring is
```{r}
round(red + blue,4)
```

## 2
A machine contains several different color balls as seen below. I found the probability using the method above.
```{r}
total = 19+20+24+17
green = 19/total
red = 20/total
blue = 24/total
yellow = 17/total

round(red,4)
```
## 3
```{r}
apartment <- c(81,228)
dorm <- c(116,79)
parents <- c(215,252)
greek <- c(130, 97)
other <- c(129, 72)
data <- data.frame(t(cbind(apartment, dorm, parents, greek, other)))
colnames(data) <- c( 'males', 'females')
round((sum(data$females)+sum(data$males)-215)/sum(data), 4)
```
## 4
Dependent 

## 5
```{r}
choose(8,3)*choose(7,3)*choose(8,1)
```
## 6
Independent.
## 7
```{r}
factorial(14)/factorial(14-8)
```
## 8

```{r}
total = 9+4+9
red = 9
orange = 4
green =  9

this = orange/total * green/(total-1) * (green -1)/(total -2) * (green-2)/(total-3)
round(this, 4)
```


## 9
$$
\frac{11!}{7!} = 11*10*9*8 = 7920
$$
```{r}
choose(11,7)
```
## 10
33% of subscribers to a fitness magazine are 34 or younger

## 11
Suppose we flip 4 coins, and win if we get exactly 3 heads. The probability of that can be expressed as 
$$ \frac{\text{Number of winning combinations}}{\text{total possibilites}} = \frac{{4}\choose{3}}{2^4} = \frac{4}{16} = \frac{1}{4} $$ 
The expected wage from 559 trials would be $$(97/4-30*3/4)*559 = 978.25$$

## 12
Suppose we flip 9 coins, and win if we get less than 5 tails. The probability of that can be expressed as 
$$ \frac{\text{Number of winning combinations}}{\text{total possibilites}} = \frac{P(\text{tails = 3})+P(\text{tails = 2})+P(\text{tails = 1})}{2^9} = \frac{{{9}\choose{1}}+{{9}\choose{2}}+{{9}\choose{3}}}{512} = \frac{129}{512} = .25
$$
The expected wage from 994 trials would be $$(23/4-26*3/4)*994 = -13667.50$$

## 13
### a
In the below problem, pass is meant to denote someone whoe does not trigger the polygraph alarm. A fail means the opposite.  
P(liar|pass) = .59  
P(truther | pass) = .90
P(liar) = .2

$$
P(A|B) = \frac{P(A \cap B)}{P(A)} \leadsto P(A \cap B) = P(A) * P(B|A) = .2*.59 = .12
$$
### b 
1- P(B|A) = .88

### c
$$ P(A) \cup P(truth | lie-detected)  = P(A) + P(truth|detected) $$


$$ P(truth|detected) = \frac{P(A\cap B)}{P(B)} = \frac{.12}{}  $$
