---
title: "605 Wk 7"
author: "simplymathematics"
date: "October 14, 2018"
output: html_document
---

# Problem 1

$X_1$, $X_2$ are mutually indeendent, random variables. They are uniformly distributed from 1 to $k$. Let $Y$ denote the minimum of the $X$. Find the distribution of $Y$. 

Since $Y$ is the minimum value of $X$ over all the $X_s$, we have enumberate the ways in which each $X$ can be assinged different values between 1 and $k$.

First, suppose that each $X$ has $k$ possibilities. Then, the total possible number of assignments for all random variables is $k^n$. This will form the denominator later.

Next, the number of ways of getting Y = 1 is $k^n-(k-1)^n$, since the first term represents the number of options and the second term represents the options were none of the $X$ are equal to 1. 

By proceeding in this manner for higher values of Y, we see that for $ 1\leq j \leq k$, and the $$ pdf(Y = j) = \frac{(k-j+1)^n - (k-j)^n}{k^n} $$

# Problem 2

An organization has a machine that is expected to work for 10 years (i.e. its failure rate is .1 failures/year). For each of the below distributions I have shown the probability statement in latex and computed the result in R to verify.

## Geometric
The geometric mass function can be given as
$$
P(X=k) = 
(1-p)^{k}p = 
\frac{.9^8}{10} = 
.043
$$
```{r}
dgeom(x = 8, prob = .1)

```
The geometric distribution has a mean given by $\frac{1}{p} = \frac{1}{.1} = 10$
with a variance of
$$
\frac{1-p}{p^2} = \frac{.9}{.01} = 90
$$

## Exponential
The exponential mass function can be given as
$$
P(X=x)
\lambda e^{-\lambda x} = 
.1e^.1*8 = 
.1e^.8 = 
.045
$$
```{r}
dexp(x = 8, rate = .1)
```
The exponential distribution has mean given by $\frac{1}{\lambda}$, or 10, with a variance of 
$(\frac{1}{10})^{-2} = 100 $. 
## Binomial
The binomial mass function can be given as
$$
P(X = k) = 
{{n}\choose{k}}p^k(1-p)^{n-k} = 
{{8}\choose{0}}.1^0(.9)^8 = 
.43
$$
```{r}
dbinom(0,8,.1)
```

The mean can be modeled by $np$, or .8. The variance can be modelled as $np(1-p)$, or $.8*.9 = .72$

## Poisson
The poisson mass function can be given as
$$
P(X = k) = 
\frac{\lambda^k e^{-\lambda}}{k!} = 
\frac{10^1 e^-10}{1!} = 
.112
$$
```{r}
dpois(x = 8, lambda = 10)
```

It's mean and variance are equal to its $\lambda$, 10. 