---
title: "605 Week 6"
author: "simplymathematics"
date: "October 3, 2018"
output: html_document
---

First, we set all of known quanities as given by the problem.

```{r}
sample.size = 1000
republican= .48
democrat = .52

```

Then, for ease of accounting, we treat Republicans as 0s and Democrats as 1. Then, we sample a population with the requisite weights, sum up that vector, and repeat 100 times. 

```{r}
# 0 is republican, 1 is democrat
rounds <- c()
for (i in 1:100){
   rounds[i]<-sum(sample(c(0, 1), size = sample.size, replace = TRUE, prob = c(republican, democrat)))/sample.size
}

length(rounds[rounds<.50])/1000



```
In the first case, our simulation incorrectly predicted the winner 1% of the time. 
```{r}
republican.2 = 49
democrat.2 = 51

rounds <- c()
for (i in 1:100){
   rounds[i]<-sum(sample(c(0, 1), size = sample.size, replace = TRUE, prob = c(republican.2, democrat.2)))/sample.size
}

length(rounds[rounds<.50])/100

```
In the second case, our simulation incorrectly predicted the winner 22% of the time.
```{r}
sample.size.2 = 3000
rounds <- c()
for (i in 1:100){
   rounds[i]<-sum(sample(c(0, 1), size = sample.size.2, replace = TRUE, prob = c(republican.2, democrat.2)))/sample.size.2
}

length(rounds[rounds<.50])/100
sort(rounds)

```
Even with a larger sample size, the smaller gap between the parties resulted in our simulation incorrectly predicted the winner 8% of the time.